experiment 1

### 2021-10-27 experiments/experiment 1/experiment-1.Rmd
Next spep - only Puzzles left

library(microxanoxBeta)
if (packageVersion("microxanoxBeta") < package_version("0.2.3")) {
  stop("microxanox version needs to be at least 0.2.3!")
}
library(tidyverse)
library(patchwork)
library(here)
source(here("R/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
options(mc.cores = 8)
eval_dynamics_flag <- TRUE
```

@@

```{r}
options(mc.cores = 8)
```

@@

Run stable state finding

@@

Process the stable state data

Bring in various stable state datasets
```{r eval = TRUE}
cluster <- multidplyr::new_cluster(7)
multidplyr::cluster_library(cluster, c("microxanoxBeta", "dplyr"))

@@

## sim length 300'000, 20 SBPBgrad, reference maximum diversity
# var_expt4 <- readRDS(here("experiments/experiment 1/data/ss_data_300000_small.RDS")) %>%
#   mutate(sim_length = 300000)
# stab_data4 <- var_expt4 %>%
#   group_by(CB_var_gmax_s, CB_var_h_s,
#            SB_var_gmax_s, SB_var_h_s,
#            PB_var_gmax_s, PB_var_h_s, sim_length) %>%
#   do(stability_measures = get_stability_measures(.$ss_res[[1]]))
# stab_data4 <- unnest(stab_data4, cols = c(stability_measures))
# saveRDS(stab_data4, here("experiments/experiment 1/data/stab_data_300000.RDS"))
readRDS(here("experiments/experiment 1/data/ss_data_300000_small.RDS")) %>%
  mutate(sim_length = 300000) %>% 
  multidplyr::partition(cluster) %>%
  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
  collect() %>%
  unnest(cols = c(stability_measures)) %>%
  saveRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))

## sim length 1'000'000, 20 SBPBgrad, 2xCB variation, 6xSBPB variation
# var_expt5 <- readRDS(here("experiments/experiment 1/data/stab_data_300000.RDS")) %>%
#   mutate(sim_length = 1000000)
# stab_data5 <- var_expt5 %>%
#   group_by(CB_var_gmax_s, CB_var_h_s,
#            SB_var_gmax_s, SB_var_h_s,
#            PB_var_gmax_s, PB_var_h_s, sim_length) %>%
#   do(stability_measures = get_stability_measures(.$ss_res[[1]]))
# stab_data5 <- unnest(stab_data5, cols = c(stability_measures))
# saveRDS(stab_data5, here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial.RDS"))
readRDS(here("experiments/experiment 1/data/stab_data_300000.RDS")) %>%
  mutate(sim_length = 1000000) %>% 
  multidplyr::partition(cluster) %>%
  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
  collect() %>%
  unnest(cols = c(stability_measures)) %>%
  saveRDS(here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial.RDS"))
```

@@

```{r}
stab_data1 <- readRDS(here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS"))
stab_data2 <- readRDS(here("experiments/experiment 1/data/stab_data_80000.RDS"))
stab_data <- bind_rows(stab_data1, stab_data2)

@@

#all_stab_results <- readRDS(here("experiments/experiment summary/all_stab.RDS"))

all_stab_results %>%
  filter(Species == "O") %>%
  ggplot(aes(x = var_gmax, y = hyst_range, col=var_treat, shape = as_factor(sim_length))) +
  geom_point() +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
  labs(col = "Variation in\nonly these\nfunctional groups")
##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)

all_stab_results %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "O",
         sim_length == 1e6) %>%
  ggplot(aes(x = var_gmax,
             ymin = hyst_min,
             ymax = hyst_max,
             fill=var_treat)) +
  geom_ribbon(alpha = 0.5) +
  facet_wrap( ~ var_treat, nrow = 3) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  labs(fill = "Variation in\nonly these\nfunctional groups") +
  coord_flip() +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
  )

all_stab_results %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "O",
         sim_length == 8e4) %>%
  ggplot(aes(x = var_gmax,
             ymin = hyst_min,
             ymax = hyst_max,
             fill=var_treat)) +
  geom_ribbon(alpha = 0.5) +
  facet_wrap( ~ var_treat, nrow = 3) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  labs(fill = "Variation in\nonly these\nfunctional groups") +
  coord_flip() +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
  )

##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
stab_data1 <- readRDS(here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS"))
stab_data_x <- readRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))
stab_data_plus <- bind_rows(stab_data1, stab_data_x)
stab_data_plus %>%
  filter(Species == "O",
         sim_length == 1e6) %>%
  ggplot(aes(x = CB_var_gmax_s, y = SB_var_gmax_s, fill = hyst_range, col = hyst_range)) +
  geom_point(size = 3)

@@

p_overlay1 <- plot_ss_result2(var_expt_x[1,]$ss_res[[1]],
                             var_expt_x[19,]$ss_res[[1]],
                             xlims = c(-7, -1))
p_overlay1

stab_data_x %>%
  filter(Species == "O") %>%
  ggplot(aes(x = SB_var_gmax_s, y = hyst_range)) +
  geom_point() +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
  labs(col = "Variation in\nonly these\nfunctional groups")
##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)

stab_data_x %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "O") %>%
  ggplot(aes(x = SB_var_gmax_s,
             ymin = hyst_min,
             ymax = hyst_max)) +
  geom_ribbon(alpha = 0.5) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  coord_flip() +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
  )

@@

#all_stab_results <- readRDS(here("experiments/experiment summary/all_stab.RDS"))

all_stab_results %>%
  filter(Species == "O") %>%
  ggplot(aes(x = var_gmax, y = hyst_range, col=var_treat, shape = as_factor(sim_length))) +
  geom_point() +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
  labs(col = "Variation in\nonly these\nfunctional groups")
##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)

all_stab_results %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "O",
         sim_length == 1e6) %>%
  ggplot(aes(x = var_gmax,
             ymin = hyst_min,
             ymax = hyst_max,
             fill=var_treat)) +
  geom_ribbon(alpha = 0.5) +
  facet_wrap( ~ var_treat, nrow = 3) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  labs(fill = "Variation in\nonly these\nfunctional groups") +
  coord_flip() +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
  )

##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
stab_data %>%
  filter(Species == "O",
         sim_length == 1e6) %>%
  ggplot(aes(x = CB_var_gmax_s, y = SB_var_gmax_s, fill = hyst_range, col = hyst_range)) +
  geom_point(size = 3)

@@

stab_data %>%
  filter(Species == "O",
         sim_length == 1e6) %>%
  ggplot(aes(x = CB_var_gmax_s, y = hyst_range, col = as.factor(SB_var_gmax_s))) +
  geom_line(size = 2)

@@

p1_long  <- plot_ss_result1(var_expt1,
                result_index = max_diversty_all,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1_long

@@

@@

```{r eval = eval_dynamics_flag}
default_sim_duration <- 100000
```

```{r eval = eval_dynamics_flag}
default_log10a_series <- c(-4.8, -4.8)
initial_state <- new_initial_state(num_CB_strains,
                                   num_PB_strains,
                                   num_SB_strains,
                                   values = "bush_ssfig3")
initial_state[grep("CB_", names(initial_state))] <- 10^10/num_CB_strains
sim_res_novar1 <- run_simulation(parameter_values = var_expt$pars[[no_diversity]],
                          initial_state = initial_state)
saveRDS(sim_res_novar1, here("experiments/experiment 1/data/puzzle1_1.RDS"))
```

>>>>

library(microxanoxBeta)
if (packageVersion("microxanoxBeta") < package_version("0.2.3")) {
  stop("microxanox version needs to be at least 0.2.3!")
}
library(tidyverse)
library(patchwork)
library(here)
source(here("R/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
options(mc.cores = 7)
eval_dynamics_flag <- TRUE
```

@@

### Setup parameter

```{r}
options(mc.cores = 7)
```

@@

### Run stable state finding

@@

### Process the stable state data

Bring in various stable state datasets
```{r eval = eval_dynamics_flag}
cluster <- multidplyr::new_cluster(7)
multidplyr::cluster_library(cluster, c("microxanoxBeta", "dplyr"))

@@

## sim length 300'000, 20 SBPBgrad, reference maximum diversity
# var_expt4 <- readRDS(here("experiments/experiment 1/data/ss_data_300000_small.RDS")) %>%
#   mutate(sim_length = 300000)
# stab_data4 <- var_expt4 %>%
#   group_by(CB_var_gmax_s, CB_var_h_s,
#            SB_var_gmax_s, SB_var_h_s,
#            PB_var_gmax_s, PB_var_h_s, sim_length) %>%
#   do(stability_measures = get_stability_measures(.$ss_res[[1]]))
# stab_data4 <- unnest(stab_data4, cols = c(stability_measures))
# saveRDS(stab_data4, here("experiments/experiment 1/data/stab_data_300000.RDS"))
readRDS(here("experiments/experiment 1/data/ss_data_300000_small.RDS")) %>%
  mutate(sim_length = 300000) %>% 
  multidplyr::partition(cluster) %>%
  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
  collect() %>%
  unnest(cols = c(stability_measures)) %>%
  saveRDS(here("experiments/experiment 1/data/stab_data_300000.RDS"))

## sim length 1'000'000, 20 SBPBgrad, 2xCB variation, 6xSBPB variation
# var_expt5 <- readRDS(here("experiments/experiment 1/data/stab_data_300000.RDS")) %>%
#   mutate(sim_length = 1000000)
# stab_data5 <- var_expt5 %>%
#   group_by(CB_var_gmax_s, CB_var_h_s,
#            SB_var_gmax_s, SB_var_h_s,
#            PB_var_gmax_s, PB_var_h_s, sim_length) %>%
#   do(stability_measures = get_stability_measures(.$ss_res[[1]]))
# stab_data5 <- unnest(stab_data5, cols = c(stability_measures))
# saveRDS(stab_data5, here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial.RDS"))
x <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS")) %>%
  mutate(sim_length = 1000000) %>% 
  multidplyr::partition(cluster) %>%
  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
  collect() %>%
  unnest(cols = c(stability_measures)) %>%
  saveRDS(here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial.RDS"))
```

@@

### Calculations
```{r}
stab_data <- bind_rows(
  readRDS(here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS")), 
  readRDS(here("experiments/experiment 1/data/stab_data_80000.RDS"))
)

@@

all_stab_results <- all_stab_results %>%
    mutate(var_treat = forcats::fct_relevel(var_treat, levels = c("CB", "SB-PB", "CB-SB-PB")))

saveRDS(all_stab_results, here("experiments/experiment 1/data/all_stab.RDS"))
```

### Plot raw
```{r}

all_stab_results <- readRDS(here("experiments/experiment summary/all_stab.RDS"))

all_stab_results %>%
  filter(Species == "O") %>%
  ggplot(aes(x = var_gmax, y = hyst_range_raw, col=var_treat, shape = as_factor(sim_length))) +
  geom_point() +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
  labs(col = "Variation in\nonly these\nfunctional groups")
##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)

all_stab_results %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "O",
         sim_length == 1e6) %>%
  ggplot(aes(x = var_gmax,
             ymin = hyst_min_raw,
             ymax = hyst_max_raw,
             fill=var_treat)) +
  geom_ribbon(alpha = 0.5) +
  facet_wrap( ~ var_treat, nrow = 3) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  labs(fill = "Variation in\nonly these\nfunctional groups") +
  coord_flip() +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
  )

all_stab_results %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "O",
         sim_length == 8e4) %>%
  ggplot(aes(x = var_gmax,
             ymin = hyst_min_raw,
             ymax = hyst_max_raw,
             fill=var_treat)) +
  geom_ribbon(alpha = 0.5) +
  facet_wrap( ~ var_treat, nrow = 3) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  labs(fill = "Variation in\nonly these\nfunctional groups") +
  coord_flip() +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
  )

bind_rows(
  readRDS(here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS")), 
  readRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))
) %>%
  filter(
    Species == "O",
    sim_length == 1e6
  ) %>%
  ggplot(aes(x = CB_var_gmax_s, y = SB_var_gmax_s, fill = hyst_range_raw, col = hyst_range_raw)) +
  geom_point(size = 3)

### Plot log
```{r}

all_stab_results <- readRDS(here("experiments/experiment summary/all_stab.RDS"))

all_stab_results %>%
  filter(Species == "O") %>%
  ggplot(aes(x = var_gmax, y = hyst_range_log, col=var_treat, shape = as_factor(sim_length))) +
  geom_point() +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
  labs(col = "Variation in\nonly these\nfunctional groups")
##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)

all_stab_results %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "O",
         sim_length == 1e6) %>%
  ggplot(aes(x = var_gmax,
             ymin = hyst_min_log,
             ymax = hyst_max_log,
             fill=var_treat)) +
  geom_ribbon(alpha = 0.5) +
  facet_wrap( ~ var_treat, nrow = 3) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  labs(fill = "Variation in\nonly these\nfunctional groups") +
  coord_flip() +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
  )

all_stab_results %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "O",
         sim_length == 8e4) %>%
  ggplot(aes(x = var_gmax,
             ymin = hyst_min_log,
             ymax = hyst_max_log,
             fill=var_treat)) +
  geom_ribbon(alpha = 0.5) +
  facet_wrap( ~ var_treat, nrow = 3) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  labs(fill = "Variation in\nonly these\nfunctional groups") +
  coord_flip() +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
  )

bind_rows(
  readRDS(here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS")), 
  readRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))
) %>%
  filter(
    Species == "O",
    sim_length == 1e6
  ) %>%
  ggplot(aes(x = CB_var_gmax_s, y = SB_var_gmax_s, fill = hyst_range_log, col = hyst_range_log)) +
  geom_point(size = 3)

@@

p_overlay1 <- plot_ss_result2(var_expt_x[1,]$ss_res[[1]],
                             var_expt_x[19,]$ss_res[[1]],
                             xlims = c(-7, -1))
p_overlay1
```

### raw
```{r}
stab_data_x %>%
  filter(Species == "O") %>%
  ggplot(aes(x = SB_var_gmax_s, y = hyst_range_raw)) +
  geom_point() +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
  labs(col = "Variation in\nonly these\nfunctional groups")
##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)

stab_data_x %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "O") %>%
  ggplot(aes(x = SB_var_gmax_s,
             ymin = hyst_min_raw,
             ymax = hyst_max_raw)) +
  geom_ribbon(alpha = 0.5) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  coord_flip() +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
  )
```

### log
```{r}
stab_data_x %>%
  filter(Species == "O") %>%
  ggplot(aes(x = SB_var_gmax_s, y = hyst_range_log)) +
  geom_point() +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
  labs(col = "Variation in\nonly these\nfunctional groups")
##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)

stab_data_x %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "O") %>%
  ggplot(aes(x = SB_var_gmax_s,
             ymin = hyst_min_log,
             ymax = hyst_max_log)) +
  geom_ribbon(alpha = 0.5) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  coord_flip() +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
  )
```

@@

#all_stab_results <- readRDS(here("experiments/experiment summary/all_stab.RDS"))
```

### raw
```{r}
all_stab_results %>%
  filter(Species == "O") %>%
  ggplot(aes(x = var_gmax, y = hyst_range_raw, col=var_treat, shape = as_factor(sim_length))) +
  geom_point() +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
  labs(col = "Variation in\nonly these\nfunctional groups")
##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)

all_stab_results %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "O",
         sim_length == 1e6) %>%
  ggplot(aes(x = var_gmax,
             ymin = hyst_min_raw,
             ymax = hyst_max_raw,
             fill=var_treat)) +
  geom_ribbon(alpha = 0.5) +
  facet_wrap( ~ var_treat, nrow = 3) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  labs(fill = "Variation in\nonly these\nfunctional groups") +
  coord_flip() +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
  )

##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
stab_data %>%
  filter(Species == "O",
         sim_length == 1e6) %>%
  ggplot(aes(x = CB_var_gmax_s, y = SB_var_gmax_s, fill = hyst_range_raw, col = hyst_range_raw)) +
  geom_point(size = 3)

@@

stab_data %>%
  filter(Species == "O",
         sim_length == 1e6) %>%
  ggplot(aes(x = CB_var_gmax_s, y = hyst_range_raw, col = as.factor(SB_var_gmax_s))) +
  geom_line(size = 2)
```

### log
```{r}
all_stab_results %>%
  filter(Species == "O") %>%
  ggplot(aes(x = var_gmax, y = hyst_range_log, col=var_treat, shape = as_factor(sim_length))) +
  geom_point() +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
  labs(col = "Variation in\nonly these\nfunctional groups")
##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)

all_stab_results %>%
  #filter(var_treat == "CB") %>%
  filter(Species == "O",
         sim_length == 1e6) %>%
  ggplot(aes(x = var_gmax,
             ymin = hyst_min_log,
             ymax = hyst_max_log,
             fill=var_treat)) +
  geom_ribbon(alpha = 0.5) +
  facet_wrap( ~ var_treat, nrow = 3) +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Oxygen diffusivity\n[log10 uM per hour]") +
  labs(fill = "Variation in\nonly these\nfunctional groups") +
  coord_flip() +
  theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
  )

##ggsave("manuscript/figures/extent_of_bistab2.pdf", height = 4)
stab_data %>%
  filter(Species == "O",
         sim_length == 1e6) %>%
  ggplot(aes(x = CB_var_gmax_s, y = SB_var_gmax_s, fill = hyst_range_log, col = hyst_range_log)) +
  geom_point(size = 3)

stab_data %>%
  filter(Species == "O",
         sim_length == 1e6) %>%
  ggplot(aes(x = CB_var_gmax_s, y = hyst_range_log, col = as.factor(SB_var_gmax_s))) +
  geom_line(size = 2)
```

@@

p1_long  <- plot_ss_result1(var_expt1,
                result_index = max_diversty_all,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1_long
```

@@

TODO CHECK THE PARAMETER

@@

```{r eval = eval_dynamics_flag}
parameter <- readRDS(here("experiments/experiment 1/data/sim_res_novar3.RDS"))
parameter$sim_duration <- 100000
parameter$result <- NULL
```

```{r eval = eval_dynamics_flag}
parameter$log10a_series <- c(-4.8, -4.8)
parameter$strain_parameter$initial_state <- new_initial_state(
  nrow(parameter$strain_parameter$CB),
  nrow(parameter$strain_parameter$PB),
  nrow(parameter$strain_parameter$PB),
  values = "bush_ssfig3"
)
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/nrow(parameter$strain_parameter$CB)

sim_res_novar1 <- run_simulation(parameter)
saveRDS(sim_res_novar1, here("experiments/experiment 1/data/puzzle1_1.RDS"))
```
